Step 13: Forest Plots - Marginal Effects and PS Methods Comparison

### 2025-09-08 reanalysis-13-forest_plots.qmd
reorganize

  ame_plot <- ggplot(data_subgroups, aes(x = AME, y = Labels)) +
    geom_vline(xintercept = 0, color = "#be123c", linetype = "solid", size = 0.5) +
    geom_point(size = 3, color = "#2563eb") +
    geom_errorbarh(aes(xmin = Lower, xmax = Upper), height = 0.2, color = "#2563eb") +
    geom_text(
      aes(x = Lower, label = sprintf("%.3f", Lower)), 
      hjust = 1.2, size = 3, color = "black"
    ) +
    geom_text(
      aes(x = Upper, label = sprintf("%.3f", Upper)), 
      hjust = -0.2, size = 3, color = "black"
    ) +
    geom_text(
      aes(x = AME, label = sprintf("%.3f", AME)), 
      vjust = -1, size = 3.5, fontface = "bold", color = "#2563eb"
    ) +
    scale_x_continuous(
      limits = c(min(data_subgroups$Lower) - 0.02, max(data_subgroups$Upper) + 0.02),
      breaks = seq(-0.1, 0.2, by = 0.05)
    ) +
    labs(
      title = "Average Marginal Effects of Lapsing Across Subgroups",
      subtitle = "Twang GBM with IPW - Pooled across 50 imputations",
      x = "Average Marginal Effect (AME)",
      y = "",
      caption = "AME > 0 indicates increased probability of vision impairment with lapsing"
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(size = 10),
      axis.text.y = element_text(size = 11, face = "bold"), 
      axis.title.x = element_text(size = 12, face = "bold", margin = margin(t = 20)),
      plot.title = element_text(size = 14, face = "bold", hjust = 0.5, margin = margin(b = 10)),
      plot.subtitle = element_text(size = 11, hjust = 0.5, margin = margin(b = 20)),
      plot.margin = margin(20, 20, 20, 20),
      panel.grid.major.y = element_line(color = "gray90", linetype = "dotted"),
      panel.grid.minor = element_blank(),
      plot.caption = element_text(size = 9, face = "italic", margin = margin(t = 20))
    )

>>>>

  ame_plot <- ggplot(data_subgroups, aes(x = AME, y = Labels)) +
    geom_vline(xintercept = 0, color = "#be123c", linetype = "solid", size = 0.5) +
    geom_point(size = 3, color = "#2563eb") +
    geom_errorbarh(aes(xmin = Lower, xmax = Upper), height = 0.2, color = "#2563eb") +
    geom_text(
      aes(x = Lower, label = sprintf("%.3f", Lower)), 
      hjust = 1.2, size = 3, color = "black"
    ) +
    geom_text(
      aes(x = Upper, label = sprintf("%.3f", Upper)), 
      hjust = -0.2, size = 3, color = "black"
    ) +
    geom_text(
      aes(x = AME, label = sprintf("%.3f", AME)), 
      vjust = -1, size = 3.5, fontface = "bold", color = "#2563eb"
    ) +
    scale_x_continuous(
      limits = c(min(data_subgroups$Lower) - 0.02, max(data_subgroups$Upper) + 0.02),
      breaks = seq(-0.1, 0.2, by = 0.05)
    ) +
    labs(
      title = "Average Marginal Effects of Lapsing Across Subgroups",
      subtitle = "Twang GBM with IPW - Pooled across 50 imputations",
      x = "Average Marginal Effect (AME)",
      y = "",
      caption = "AME > 0 indicates increased probability of vision impairment with lapsing"
    ) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(size = 10),
      axis.text.y = element_text(size = 11, face = "bold"), 
      axis.title.x = element_text(size = 12, face = "bold", margin = ggplot2::margin(t = 20)),
      plot.title = element_text(size = 14, face = "bold", hjust = 0.5, margin = ggplot2::margin(b = 10)),
      plot.subtitle = element_text(size = 11, hjust = 0.5, margin = ggplot2::margin(b = 20)),
      plot.margin = ggplot2::margin(20, 20, 20, 20),
      panel.grid.major.y = element_line(color = "gray90", linetype = "dotted"),
      panel.grid.minor = element_blank(),
      plot.caption = element_text(size = 9, face = "italic", margin = margin(t = 20))
    )
